---
title: "Thesis Mediation models: Youth to mentors"
output: 
  html_notebook:
    toc: yes
    toc_float: yes
---

# Introduction
This R notebook is in relation to part 2 of Neil Yetz's Thesis. In this notebook, Run a series of mediation models to see if belongingness serves as a mediator between inbound/outbound connections and several program outcomes (Academic aspirations[asp], Depression[dep], Anger[anger], and delinquency[dlq]).

This notebook utilizes the data of inbound and outbound connections that youth feel with their ***ANY MENTOR***


# Clear environment
```{r}
rm(list = ls())
```


# Load libraries
```{r, message = FALSE}
library(tidyverse)
library(olsrr)
library(psych)
```

# Read in data
```{r, message = FALSE}
mens <- read_csv("../Data/Final_datasets/mens_final.csv")
```

# Factor income (For dummy code)
```{r}
mens <- mutate(mens, income = as.factor(income))
```


# describe data
```{r}
describe(mens)
```


# Inbound Models
## Model 1 kids: Academic aspriation
### Model.xy (nonsig)
```{r}
model.xy <- lm(asp_5 ~ inbound4 + kage +  mentee_male + income + dessa_0 + asp_0, data=mens)
ols_regress(model.xy)
```
### Model.xm (nonsig)
```{r}
model.xm <- lm(belong_4 ~ inbound4 + kage +  mentee_male + income + dessa_0 + asp_0 , data=mens)
ols_regress(model.xm)
```

### Model.xmy (Did not run)


## Model 2 kids: Depression
### Model.xy (nonsig)
```{r}
model.xy <- lm(cesd_5 ~ inbound4 + kage +  mentee_male + income + dessa_0 + cesd_0, data=mens)
ols_regress(model.xy)
```
### Model.xm (nonsig)
```{r}
model.xm <- lm(belong_4 ~ inbound4 + kage +  mentee_male + income + dessa_0 + cesd_0 , data=mens)
ols_regress(model.xm)
```

### Model.xmy (Did not run)



## Model 3 kids: Anger
### Model.xy (nonsig)
```{r}
model.xy <- lm(anger_5 ~ inbound4 + kage +  mentee_male + income + dessa_0 + anger_0, data=mens)
ols_regress(model.xy)
```
### Model.xm (nonsig)
```{r}
model.xm <- lm(belong_4 ~ inbound4 + kage +  mentee_male + income + dessa_0 + cesd_0 , data=mens)
ols_regress(model.xm)
```

### Model.xmy (Did not run)

## Model 4 kids: Delinquency
### Model.xy (nonsig)
```{r}
model.xy <- lm(dlq_5 ~ inbound4 + kage +  mentee_male + income + dessa_0 + dlq_0, data=mens)
ols_regress(model.xy)
```
### Model.xm (nonsig)
```{r}
model.xm <- lm(belong_4 ~ inbound4 + kage +  mentee_male + income + dessa_0 + dlq_0 , data=mens)
ols_regress(model.xm)
```

### Model.xmy (Did not run)


# Outbound Models

## Model 1 kids: Academic aspriation
### Model.xy (sig)
```{r}
model.xy <- lm(asp_5 ~ outbound4 + kage +  mentee_male + income + dessa_0 + asp_0, data=mens)
ols_regress(model.xy)
```
### Model.xm (sig)
```{r}
model.xm <- lm(belong_4 ~ outbound4 + kage +  mentee_male + income + dessa_0 + asp_0 , data=mens)
ols_regress(model.xm)
```

### Model.xmy (nonsig)
```{r}
model.xmy <- lm(asp_5 ~ outbound4 + belong_4 + kage +  mentee_male + income + dessa_0 + asp_0 , data=mens)
ols_regress(model.xmy)
```

## Model 2 kids: Depression
### Model.xy (nonsig)
```{r}
model.xy <- lm(cesd_5 ~ outbound4 + kage +  mentee_male + income + dessa_0 + cesd_0, data=mens)
ols_regress(model.xy)
```
### Model.xm (sig)
```{r}
model.xm <- lm(belong_4 ~ outbound4 + kage +  mentee_male + income + dessa_0 + cesd_0 , data=mens)
ols_regress(model.xm)
```

### Model.xmy (sig mediator)
```{r}
model.xmy <- lm(cesd_5 ~ outbound4 + belong_4 + kage +  mentee_male + income + dessa_0 + cesd_0, data=mens)
ols_regress(model.xmy)
```


## Model 3 kids: Anger
### Model.xy (nonsig)
```{r}
model.xy <- lm(anger_5 ~ outbound4 + kage +  mentee_male + income + dessa_0 + anger_0, data=mens)
ols_regress(model.xy)
```
### Model.xm (sig)
```{r}
model.xm <- lm(belong_4 ~ outbound4 + kage +  mentee_male + income + dessa_0 + cesd_0 , data=mens)
ols_regress(model.xm)
```

### Model.xmy (nonsig)
```{r}
model.xmy <- lm(anger_5 ~ outbound4 + belong_4 + kage +  mentee_male + income + dessa_0 + anger_0, data=mens)
ols_regress(model.xmy)
```



## Model 4 kids: Delinquency
### Model.xy (nonsig)
```{r}
model.xy <- lm(dlq_5 ~ outbound4 + kage +  mentee_male + income + dessa_0 + dlq_0, data=mens)
ols_regress(model.xy)
```
### Model.xm (sig)
```{r}
model.xm <- lm(belong_4 ~ outbound4 + kage +  mentee_male + income + dessa_0 + dlq_0 , data=mens)
ols_regress(model.xm)
```

### Model.xmy (nonsig)
```{r}
model.xmy <- lm(dlq_5 ~ outbound4 + belong_4 + kage +  mentee_male + income + dessa_0 + dlq_0, data=mens)
ols_regress(model.xmy)
```




