---
title: "Thesis Mediation models: Youth to primary mentor"
output: 
  html_notebook:
    toc: yes
    toc_float: yes
    toc_depth: 4
---

# Introduction
This R notebook is in relation to part 2 of Neil Yetz's Thesis. In this notebook, Run a series of mediation models to see if belongingness serves as a mediator between inbound/outbound connections and several program outcomes (Academic aspirations[asp], Depression[dep], Anger[anger], and delinquency[dlq]).

This notebook utilizes the data of inbound and outbound connections that youth feel with their ***PRIMARY MENTOR***


# Clear environment
```{r}
rm(list = ls())
```


# Load libraries
```{r, message = FALSE}
library(tidyverse)
library(olsrr)
library(psych)
library(RMediation)
```

# Read in data
```{r, message = FALSE}
pmen <- read_csv("../Data/Final_datasets/pmens_final.csv")
```

# Factor income (For dummy code)
```{r}
pmen <- mutate(pmen, income = as.factor(income))
```


# describe data
```{r}
describe(pmen)
```


# Inbound Models
## Model 1 kids: Academic aspriation
### Model.xy (sig)
```{r}
model.xy <- lm(asp_5 ~ inbound4 + kage +  mentee_male + income + dessa_0 + asp_0, data=pmen)
ols_regress(model.xy)
```
### Model.xm (nonsig)
```{r}
model.xm <- lm(belong_4 ~ inbound4 + kage +  mentee_male + income + dessa_0 + asp_0 , data=pmen)
ols_regress(model.xm)
```

### Model.xmy (sig main predictor)
```{r}
model.xmy <- lm(asp_5 ~ inbound4 + belong_4 + kage +  mentee_male + income + dessa_0 + asp_0, data=pmen)
ols_regress(model.xmy)
```

## ***Model 2 kids: Depression***
### Model.xy (sig)
```{r}
model.xy <- lm(cesd_5 ~ inbound4 + kage +  mentee_male + income + dessa_0 + cesd_0, data=pmen)
ols_regress(model.xy)
```
### Model.xm (approaching sig)
```{r}
model.xm <- lm(belong_4 ~ inbound4 + kage +  mentee_male + income + dessa_0 + cesd_0 , data=pmen)
ols_regress(model.xm)
```

### Model.xmy (sig!)
```{r}
model.xmy <- lm(cesd_5 ~ inbound4 + belong_4 + kage +  mentee_male + income + dessa_0 + cesd_0, data=pmen)
ols_regress(model.xmy)
```


#### Pull out a and b paths
```{r}
path.a   <- coefficients(model.xm)["inbound4"]
path.b   <- coefficients(model.xmy)["belong_4"]
se.path.a<-sqrt(vcov(model.xm)["inbound4","inbound4"])
se.path.b<-sqrt(vcov(model.xmy)["belong_4","belong_4"])

path.a   
path.b   
se.path.a
se.path.b


```

#### Calculate indirect effect
```{r}
ab <- path.a*path.b
ab
```


#### Indirect effect significance test (PRODCLIN;  Non-significant)
```{r}
medci(path.a, path.b, se.path.a, se.path.b, alpha = 0.05, plot = TRUE, plotCI = TRUE)
```

#### Bootstrapping significance
```{r}


library(boot)


boot.med <- function(data, indices){
data <-data[indices,]
model.xm <- lm(belong_4 ~ inbound4 + kage +  mentee_male + income + dessa_0 + cesd_0 , data=data)
model.xmy <- lm(cesd_5 ~ inbound4 + belong_4 + kage +  mentee_male + income + dessa_0 + cesd_0, data=data)
path.a <- coefficients(model.xm)["inbound4"] #the a-path coefficient
path.b <- coefficients(model.xmy)["belong_4"] #the b-path coefficient
ab <- path.a*path.b #returns the product of a*b
return(ab)
}

medboot<-boot(data=pmen, statistic = boot.med, R = 10000)
medconfint <- boot.ci(medboot, index=1, conf = (.95), type = "bca")
print (medconfint)
plot(medboot)
```




## Model 3 kids: Anger
### Model.xy (nonsig)
```{r}
model.xy <- lm(anger_5 ~ inbound4 + kage +  mentee_male + income + dessa_0 + anger_0, data=pmen)
ols_regress(model.xy)
```
### Model.xm (nonsig)
```{r}
model.xm <- lm(belong_4 ~ inbound4 + kage +  mentee_male + income + dessa_0 + cesd_0 , data=pmen)
ols_regress(model.xm)
```

### Model.xmy (Did not run)

## Model 4 kids: Delinquency
### Model.xy (nonsig)
```{r}
model.xy <- lm(dlq_5 ~ inbound4 + kage +  mentee_male + income + dessa_0 + dlq_0, data=pmen)
ols_regress(model.xy)
```
### Model.xm (nonsig)
```{r}
model.xm <- lm(belong_4 ~ inbound4 + kage +  mentee_male + income + dessa_0 + dlq_0 , data=pmen)
ols_regress(model.xm)
```

### Model.xmy (Did not run)


# Outbound Models

## Model 1 kids: Academic aspriation
### Model.xy (approaching sig)
```{r}
model.xy <- lm(asp_5 ~ outbound4 + kage +  mentee_male + income + dessa_0 + asp_0, data=pmen)
ols_regress(model.xy)
```
### Model.xm (sig)
```{r}
model.xm <- lm(belong_4 ~ outbound4 + kage +  mentee_male + income + dessa_0 + asp_0 , data=pmen)
ols_regress(model.xm)
```

### Model.xmy (nonsig)
```{r}
model.xmy <- lm(asp_5 ~ outbound4 + belong_4 + kage +  mentee_male + income + dessa_0 + asp_0 , data=pmen)
ols_regress(model.xmy)
```

## Model 2 kids: Depression
### Model.xy (nonsig)
```{r}
model.xy <- lm(cesd_5 ~ outbound4 + kage +  mentee_male + income + dessa_0 + cesd_0, data=pmen)
ols_regress(model.xy)
```
### Model.xm (sig)
```{r}
model.xm <- lm(belong_4 ~ outbound4 + kage +  mentee_male + income + dessa_0 + cesd_0 , data=pmen)
ols_regress(model.xm)
```

### Model.xmy (sig mediator)
```{r}
model.xmy <- lm(cesd_5 ~ outbound4 + belong_4 + kage +  mentee_male + income + dessa_0 + cesd_0, data=pmen)
ols_regress(model.xmy)
```


## Model 3 kids: Anger
### Model.xy (nonsig)
```{r}
model.xy <- lm(anger_5 ~ outbound4 + kage +  mentee_male + income + dessa_0 + anger_0, data=pmen)
ols_regress(model.xy)
```
### Model.xm (sig)
```{r}
model.xm <- lm(belong_4 ~ outbound4 + kage +  mentee_male + income + dessa_0 + cesd_0 , data=pmen)
ols_regress(model.xm)
```

### Model.xmy (nonsig)
```{r}
model.xmy <- lm(anger_5 ~ outbound4 + belong_4 + kage +  mentee_male + income + dessa_0 + anger_0, data=pmen)
ols_regress(model.xmy)
```



## Model 4 kids: Delinquency
### Model.xy (nonsig)
```{r}
model.xy <- lm(dlq_5 ~ outbound4 + kage +  mentee_male + income + dessa_0 + dlq_0, data=pmen)
ols_regress(model.xy)
```
### Model.xm (sig)
```{r}
model.xm <- lm(belong_4 ~ outbound4 + kage +  mentee_male + income + dessa_0 + dlq_0 , data=pmen)
ols_regress(model.xm)
```

### Model.xmy (nonsig)
```{r}
model.xmy <- lm(dlq_5 ~ outbound4 + belong_4 + kage +  mentee_male + income + dessa_0 + dlq_0, data=pmen)
ols_regress(model.xmy)
```




